---
title: "Project"
author: "Ong Chen Yu, Neo Jia Hui"
date: "10/15/2020"
output: 
  html_document:
    theme: journal
    highlight: monochrome
    toc: true
    toc_float: true
    toc_depth: 4
    code_folding: show
    number_section: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# IS415 Geospatial Analytics Project

# Title
Spatial Analysis of the Distribution Pattern of Healthcare Facilities and Amenities in Singapore Using Geographic Information Analysis

# Problem & Motivation
Aging population has always been a prominent issue in Singapore. The percentage of individuals over age 65 between 2010 and 2020 increased from 9% to 15.2%. By 2030, one in four Singaporeans will be aged 65 and above. While there are many efforts by the government to solve this problem, it is inevitable that people will age and all of us will grow old one day.

However, in this small city-state, would its current urban landscape be enough to support its elderly?

It is essential that relevant facilities and amenities are strategically built and readily available for elderly in this land-scarce Singapore.

# Objectives
Through this project, we aim to build a Shiny application to:

- Analyse the supply and demand of age-friendly amenities and facilities in subzone planning area

- Analyse the availability of age-friendly amenities and facilities in subzone planning area

- Determine which areas needs more age-friendly amenities and facilities


# Installing and Loading Required Packages
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
packages = c('tmap', 'tidyverse','rvest','stringr','rebus','lubridate','janitor',
             'sf', 'sp', 'caret',
             'geojsonio', 'stplanr',
             'reshape2', 'broom')

for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

# Scraping data from MOH website
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
# url <-'https://www.moh.gov.sg/upcoming-and-completed-healthcare-facilities'
# content <- read_html(url)
# tables <- content %>% html_table(fill = TRUE)
# length(tables)
# first_table <- tables[[1]]
# 
# for (item in tables){
#   names = item[2]
#   adds = item[3]
#   status = item[4]
# }
```

```{r}
# Scraping test (from ah kam's link)
# get_item <- function(html){
#       html %>%
#         # The relevant tag
#         html_nodes('.sfContentBlock') %>%
#         html_text() %>%
#         # Trim additional white space
#         str_trim() %>%
#         # Convert the list into a vector
#         unlist()
# }
# get_data_table <- function(html){
#       item <- get_item(html)
#       # Combine into a tibble
#       combined_data <- tibble(items = item) 
#     }
# get_data_from_url <- function(url){
#     html <- read_html(url)
#     get_data_table(html, company_name)
#   }
# scrape_write_table <- function(url){
# 
#       page <- read_html(url)
# 
#       # Extract the number of pages that have to be queried
#       # latest_page_number <- get_last_page(first_page)
# 
#       # Generate the target URLs
#       # list_of_pages <- str_c(url, '?page=', 1:latest_page_number)
# 
#       # Apply the extraction and bind the individual results back into one table,
#       # which is then written as a tsv file into the working directory
#       page %>%
#         # Apply to all URLs
#         map(get_data_from_url) %>%
#         # Combine the tibbles into one tibble
#         bind_rows() %>%
#         # Write a tab-separated file
#         write_tsv(str_c('.tsv'))
# }
# scrape_write_table(url)
# moh_data <- read_tsv('MOH.tsv')
# tail(moh_data, 5)
```


# Data Wrangling

## Loading in Geospatial Data
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
mpsz <- st_read(dsn = "data",
                layer = "MP14_SUBZONE_WEB_PL")
popdata <- read_csv("data/respopagesextod2011to2020.csv")
eldercare <- st_read("data/ELDERCARE.kml")
chas_clinic <- st_read("data/chas-clinics-kml.kml")
community_club <- st_read("data/community-clubs-kml.kml")
```

## Loading in Aspatial Data
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
popdata <- read_csv("data/respopagesextod2011to2020.csv")
```

## Transforming the Projection
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
mpsz3414 <- st_transform(mpsz, 3414)
st_crs(mpsz3414)
```

```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
eldercare3414 <- st_transform(eldercare, 3414)
st_crs(eldercare3414)
```

```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
chas_clinic3414 <- st_transform(chas_clinic, 3414)
st_crs(chas_clinic3414)
```

```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
community_club3414 <- st_transform(community_club, 3414)
st_crs(community_club3414)
```

## Checking for Missing Values
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
sum(is.na(mpsz3414))
sum(is.na(popdata))
sum(is.na(eldercare3414))
sum(is.na(chas_clinic3414))
sum(is.na(community_club3414))
```

## Extracting 2020 Population Data
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
population20 <- popdata %>%
  filter(Time == 2020)
```

```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
population20_tidy <- population20 %>%
  group_by(PA, SZ, AG) %>%
  summarise(`POP` = sum(`Pop`)) %>%
  ungroup() %>%
  pivot_wider(names_from = AG, values_from = POP) %>%
  mutate(TOTAL = rowSums(.[3:21]))

glimpse(population20_tidy)
```

```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
pop20 <- population20_tidy %>%
  mutate(`5_to_6` = `5_to_9` * perc20) %>%
  mutate(`0_to_6` = round(`0_to_4` + `5_to_6`)) %>%
  dplyr::select(PA, SZ, `0_to_6`, TOTAL)
  
glimpse(pop20)
```

## Calculating the Supply of Eldercare Services in Each Planning Subzone
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
mpsz3414$`ELDERCARE` <- lengths(st_intersects(mpsz3414, eldercare3414))
```

## Visualising the Supply of Eldercare Services at the Planning Subzone Level
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
tm_shape(mpsz3414)+
  tm_fill(col = "ELDERCARE",
          palette = "Blues",
          style = "jenks") +
  tm_layout(main.title = "Supply of Eldercare Services at the Planning Subzone Level",
            main.title.position = "center",
            main.title.size = 1,
            legend.height = 0.45, 
            legend.width = 0.35,
            legend.outside = FALSE,
            legend.position = c("right", "bottom"),
            frame = FALSE) +
  tm_borders(alpha = 0.5)
```

## Calculating the Supply of CHAS Clinics in Each Planning Subzone
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
mpsz3414$`CLINICS` <- lengths(st_intersects(mpsz3414, chas_clinic3414))
```

## Visualising the Supply of CHAS Clinics at the Planning Subzone Level
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
tm_shape(mpsz3414)+
  tm_fill(col = "CLINICS",
          palette = "Blues",
          style = "jenks") +
  tm_layout(main.title = "Supply of CHAS Clinics at the Planning Subzone Level",
            main.title.position = "center",
            main.title.size = 1,
            legend.height = 0.45, 
            legend.width = 0.35,
            legend.outside = FALSE,
            legend.position = c("right", "bottom"),
            frame = FALSE) +
  tm_borders(alpha = 0.5)
```

## Calculating the Supply of Community Clubs in Each Planning Subzone
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
mpsz3414$`COMMUNITY_CLUBS` <- lengths(st_intersects(mpsz3414, community_club3414))
```

## Visualising the Supply of Community Clubs at the Planning Subzone Level
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
tm_shape(mpsz3414)+
  tm_fill(col = "COMMUNITY_CLUBS",
          palette = "Blues",
          style = "jenks") +
  tm_layout(main.title = "Supply of CHAS Clinics at the Planning Subzone Level",
            main.title.position = "center",
            main.title.size = 1,
            legend.height = 0.45, 
            legend.width = 0.35,
            legend.outside = FALSE,
            legend.position = c("right", "bottom"),
            frame = FALSE) +
  tm_borders(alpha = 0.5)
```


#
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
```


#
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
```


#
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
```


#
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
```


#
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE }
```




